Computing Entropies with Nested Sampling

### 2017-10-17 talk/ms.tex
Thanks

% New slide
\begin{frame}
\frametitle{Some entropies in Bayesian statistics}
Written them in terms of parameters $\theta$ and data
$d$, for Bayesian purposes.

@@

We might want to know {\em how relevant the data is to the parameters},
before learning the data. We might want to optimise that quantity for
experimental design. But it's nasty, especially if there's nuisance
parameters.
\end{frame}

@@

The number of NS iterations taken
to enter a small region (defined by a likelihood threshold) 
as an unbiased estimator of the log-probability
of that region!\vspace{0.7em}

@@

>>>>

% New slide
\begin{frame}
\frametitle{Some entropies in Bayesian statistics}
Written in terms of parameters $\theta$ and data
$d$, for Bayesian purposes.

@@

We might want to know {\em how relevant the data is to the parameters},
before learning the data. We might want to optimise that quantity for
experimental design. But it's nasty, especially if there are nuisance
parameters.
\end{frame}

@@

The number of NS iterations taken
to enter a small region (defined by a likelihood threshold) 
is an unbiased estimator of the log-probability
of that region!\vspace{0.7em}

@@

% New slide
\begin{frame}
\frametitle{Thanks}

Ruth Angus (Flatiron Institute),
Ewan Cameron (Oxford), James Curran (Auckland), Tom Elliott (Auckland),
David Hogg (NYU), Kevin Knuth (SUNY Albany),
Thomas Lumley (Auckland),
Iain Murray (Edinburgh), John Skilling
(Maximum Entropy Data Consultants), Jared Tobin ({\tt jtobin.io}).
